On Adding Pattern Matching to Haskell-based Deeply Embedded Domain Specific Languages\\ \large{Not For Distribution}

### 2020-08-01 paper/paper.tex
Different wording in tail rec description
wibble

In the technique presented here, we do not need to allocate thunks or closures.
We actually do not need to use higher-order functions at all in this tail recursion
representation.

In the \ttt{E} type of our DSL, these types of data structures are used to represent tail 
recursion by using the following constructors.

@@

We first translate this to use the \verb|Iter| type. The lambda is brought
inside of the \ttt{internalize (externalize ...)} call and wrapped in a call to
\ttt{runIter}. This inner expression is then eta expanded. Finally, each \verb|case|
branch which does not contain a recursive call is wrapped in a \verb|Done| and
every recursive call is substitute for an application of the \verb|Step| constructor.

>>>>

In the technique presented here, we do not need to allocate thunks or closures.
We do not need to use higher-order functions for this representation, other than \ttt{runIter} itself.

In the \ttt{E} type of our DSL, this form of tail recursion representation is
given a deep embedding by the following constructors:

@@

We first transform this to use the \verb|Iter| type. The lambda is brought
inside of the \ttt{internalize (externalize ...)} call and wrapped in a call to
\ttt{runIter}. This inner expression is then eta expanded. Finally, each \verb|case|
branch which does not contain a recursive call is wrapped in a \verb|Done| and
every recursive call is transformed into an application of the \verb|Step| constructor.
